Cannibalism among the supermassive black holes

### 2018-08-19 paper.tex
Added reference to Middleton 2018, etc.

\section{Introduction}\label{sec:introduction}
What happens to the massive black holes centrally located in galaxies when those galaxies merge with others?  There are three possibilities: they merge, they are ejected, or they remain in orbit in the merged galaxy.  Combinations of these options are also possible with the spin induced kick at merger leading to an ejection or extended orbit of the merged black hole.  We now know from pulsar timing measurements (ADD REFERENCES) that the gravitational wave background is probably too low for most galaxy mergers (mass-weighted) (BUT SEE MIDDLETON ET AL 2018) to lead to BH mergers, but the outcome remains uncertain.  We will argue in this paper that a very common outcome--especially for the lower mass black holes--is for the injected objects to remain as orbiting X-ray sources in normal massive galaxies waiting to be identified by current observational techniques.

>>>>

\section{Introduction}\label{sec:introduction}
What happens to the massive black holes centrally located in galaxies when those galaxies merge with others?  There are three possibilities: they merge, they are ejected, or they remain in orbit in the merged galaxy.  Combinations of these options are also possible with the spin induced kick at merger leading to an ejection or extended orbit of the merged black hole.  We now know from pulsar timing measurements (ADD REFERENCES) that the gravitational wave background is probably too low for most galaxy mergers (mass-weighted) (but see \cite{2018NatCo...9..573M}) to lead to BH mergers, but the outcome remains uncertain.  We will argue in this paper that a very common outcome--especially for the lower mass black holes--is for the injected objects to remain as orbiting X-ray sources in normal massive galaxies waiting to be identified by current observational techniques.
